\ab{Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations}

### 2021-03-18 papers/intro_paper/discussion.tex
changes in Sec. V

\ab{Furthermore, when assuming that the deviations from GR do not vary appreciably over the GW events 
that we have analyzed, and combine the likelihood functions, we have obtained the most stringent bounds  
on the dominant QNM $(\df{220}=0.02^{+0.03}_{-0.03}, \dtau{220}=0.11^{+0.12}_{-0.12})$. Those 
constraints are compatible, but sligthly better (especially for the decay time) that the ones recently reported in Ref.~\cite{Carullo:2021dui} 
(see first row in Table II therein), where measurements on QNMs were done using only the post-merger part of 
the signal, and included a larger set of GW events from O1, O2 and O3a.}

>>>>

\ab{Furthermore, when assuming that the deviations from GR do not vary appreciably over the GW events 
that we have analyzed, and combine the likelihood functions, we have obtained the most stringent bounds  
on the dominant QNM $(\df{220}=0.02^{+0.03}_{-0.03}, \dtau{220}=0.11^{+0.12}_{-0.12})$. Those 
constraints are compatible, but sligthly better (especially for the decay time) than the ones recently reported in Ref.~\cite{Carullo:2021dui} 
(see first row in Table II therein), where QNM frequencies were inferred using only the post-merger part of 
the signal. We note that Ref.~\cite{Carullo:2021dui} used a larger set of GW events from O1, O2 and O3a than we did, although we expect 
that the extra GW events will not contribute significantly to the combined bound since they have lower SNRs.}
